---
title: "code book for har smart phone data set "
date: "Sunday, August 24, 2014"
output: html_document
---

Feature Selection 
=================

The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals tAcc-XYZ and tGyro-XYZ. These time domain signals (prefix 't' to denote time) were captured at a constant rate of 50 Hz. Then they were filtered using a median filter and a 3rd order low pass Butterworth filter with a corner frequency of 20 Hz to remove noise. Similarly, the acceleration signal was then separated into body and gravity acceleration signals (tBodyAcc-XYZ and tGravityAcc-XYZ) using another low pass Butterworth filter with a corner frequency of 0.3 Hz. 

Subsequently, the body linear acceleration and angular velocity were derived in time to obtain Jerk signals (tBodyAccJerk-XYZ and tBodyGyroJerk-XYZ). Also the magnitude of these three-dimensional signals were calculated using the Euclidean norm (tBodyAccMag, tGravityAccMag, tBodyAccJerkMag, tBodyGyroMag, tBodyGyroJerkMag). 

Finally a Fast Fourier Transform (FFT) was applied to some of these signals producing fBodyAcc-XYZ, fBodyAccJerk-XYZ, fBodyGyro-XYZ, fBodyAccJerkMag, fBodyGyroMag, fBodyGyroJerkMag. (Note the 'f' to indicate frequency domain signals). 

These signals were used to estimate variables of the feature vector for each pattern:  
'-XYZ' is used to denote 3-axial signals in the X, Y and Z directions.



```{r}
Data.Book.Smart.Phone.Data1 <- read.csv("./Data-Book-Smart-Phone-Data1.csv")
Data.Book.Smart.Phone.Data1$Column.Name
Data.Book.Smart.Phone.Data1$Description.Acceleration..and.Gyroscope.readings.for.30.Subjects
```




You can also embed plots, for example:




```{r, echo=FALSE}
plot(cars)
```




Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.





