---
title: "read me for har smart phone data set "
date: "Sunday, August 24, 2014"
output: html_document
---

This Project is for the Coursera Getting and Cleaning Data class to get information about the project see:

<http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones>.

To download the data set use the following link:

<https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip>.


 You should create one R script called run_analysis.R that does the following. 

    Merges the training and the test sets to create one data set.
    Extracts only the measurements on the mean and standard deviation for each measurement. 
    Uses descriptive activity names to name the activities in the data set
    Appropriately labels the data set with descriptive variable names. 
    Creates a second, independent tidy data set with the average of each variable for each activity and each subject. 
    
    

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.